Machine Learning Methods for Discourse Segmentation of Communications in E-Mail Based Behavioral Interventions

### 2018-07-28 paper-amia-summit-2018/manuscript.tex
update methods section

\textbf{Conditional Random Fields}: CRF have been widely used in various NLP tasks including part-of-speech tagging and segmentation tasks \cite{lafferty2001conditional, hirohata2008identifying}. Unlike a maximum entropy markov model which uses per-state exponential models for the conditional probabilities of next states given the current state, a CRF is a discriminative model of the conditional distribution of the entire sequence of labels given the observation sequence. A traditional linear-chain CRF model is defined as a conditional probability distribution $p(y|x)$ for output and input sequences, $y$ and $x$, by the following equation:

\begin{equation}
p(y|x) = \frac{1}{Z_x}\exp{\left(\sum_{t=1}^{T}\sum_{k}^{}\lambda_k f_k(y_{t-1}, y_t, x, t)\right)} \\
\end{equation}

@@

\textbf{Multilayer Perceptrons}: MLP is a feed-forward artificial neural network model which maps set of input onto a set of appropriate output. This study utilized MLP with a nonlinear activation function (relu) and one hidden layer consisting of 128 hidden units. In order to prevent over-fitting, we implement dropout on fully connected layers, which randomly hide some neurons during the training phase \cite{srivastava2014dropout}. Dropout is also applied in the fully connected layers in BRNN and CRNN models. For a given sample with $2l$ words/punctuations, the first layer input of MLP was created by the summation of first $l$ word vectors and last $l$ word vectors.

@@

\textbf{Convolutional Recurrent Neural Networks}: CRNN is a deep neural network architecture consisting of 5 layers: 1) input layer 2) embedding layer 3) convolution layer with max pooling 4) BRNN layer 5) fully connected layer with dropout and sigmoid output.

>>>>

\textbf{Conditional Random Fields}: CRF have been widely used in various NLP tasks including part-of-speech tagging and segmentation tasks \cite{lafferty2001conditional, hirohata2008identifying}. Unlike a maximum entropy markov model which uses per-state exponential models for the conditional probabilities of next states given the current state, a CRF is a discriminative model of the conditional distribution of the entire sequence of labels given the observation sequence. A traditional linear-chain CRF model is defined as a conditional probability distribution $p(y|x)$ for output and input sequences, $y$ and $x$, by the Eq. \ref{Eq:crf}

\begin{equation}
\label{Eq:crf}
p(y|x) = \frac{1}{Z_x}\exp{\left(\sum_{t=1}^{T}\sum_{k}^{}\lambda_k f_k(y_{t-1}, y_t, x, t)\right)} \\
\end{equation}

@@

\textbf{Multilayer Perceptrons}: MLP is a feed-forward artificial neural network model which maps set of input onto a set of appropriate output. This study utilized MLP with a nonlinear activation function (relu) and one hidden layer consisting of 128 hidden units. In order to prevent over-fitting, we implement dropout on fully connected layers, which randomly hide some neurons during the training phase \cite{srivastava2014dropout}. Dropout is also applied in the fully connected layers in BRNN and CRNN models. For a given sample with $2l$ words/punctuations, the first layer input of MLP was created by the summation of first $l$ word vectors and last $l$ word vectors. Figure~\ref{fig:length-mlp} demostrates the performance of MLP model on e-Coaching email segmentation by varying value of $l$.

@@

\textbf{Convolutional Recurrent Neural Networks}: CRNN is a deep neural networks architecture, shown in Figure~\ref{fig:crnn}, consisting of 5 layers: 1) input layer 2) embedding layer 3) convolution layer with max pooling 4) BRNN layer 5) fully connected layer with dropout and sigmoid output.
